The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-02 rational.tex
_

\usepackage{graphicx}
%%\usepackage{longtable}
%%\usepackage{comment}
\usepackage{amsmath}
%%\usepackage{mdwlist}
%%\usepackage{txfonts}
\usepackage{xspace}
%%\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{multicol}
\usepackage[nodayofweek]{datetime}
\usepackage{etex}
\usepackage[all, cmtip]{xy}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{multicol}
\newcommand\hmmax{0} % default 3
\newcommand\bmmax{0} % default 4
\usepackage{bm}
\usepackage{cmll}

@@

\item
Associativity is entirely skipped in the graphical language. Hence
three parallel wires maybe inferred as {{b1*(b2*b3)}} or
{{(b1*b2)*b3}}, based on the context. This is much like handling of
associativity in the graphical representations of categories
\cite{springerlink:10.1007/978-3-642-12821-94},

@@

\item
Identity morphisms and their duals are represented as follows:

@@

@@

%%%%%%%%%%%%%%%%%%
\subsection{Syntax}

@@

>>>>

\usepackage{graphicx}
%%\usepackage{longtable}
\usepackage{comment}
\usepackage{amsmath}
%%\usepackage{mdwlist}
%%\usepackage{txfonts}
\usepackage{xspace}
%%\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{multicol}
\usepackage[nodayofweek]{datetime}
\usepackage{etex}
\usepackage[all, cmtip]{xy}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{multicol}
\newcommand\hmmax{0} % default 3
\newcommand\bmmax{0} % default 4
\usepackage{bm}
\usepackage{cmll}

@@

\item
Associativity is entirely implicit in the graphical language. Three
parallel wires maybe inferred as {{b1*(b2*b3)}} or {{(b1*b2)*b3}},
based on the context, much like handling of associativity in the
graphical representations of categories
\cite{springerlink:10.1007/978-3-642-12821-94}.

@@

\item
Identity morphisms and their duals ({{uniti, unite, zeroi}} and
{{zeroe}}) are represented as follows:

@@

Since the monoidal units cxan be freely introduced and eliminated, in
many diagrams they are omitted and dealt with explicitely when they
are of special interest.

@@

\begin{comment}
%%%%%%%%%%%%%%%%%%
\subsection{Syntax}

@@

\end{comment}
